Bayesian methods for black hole merger parameter estimation with LISA.

### 2018-06-02 docs/paper_PE.tex

-- High-mass system, non-degenerate, 22 and HM + Fisher - stacked SNR contours
eg:
m1,    m2,    t0,D,     phi0,i,   lam,  bet, psi
8.89e5,1.11e5,0, 3.67e4,pi/3,pi/2,3pi/4,pi/3,pi/3

>>>>

-- High-mass system, non-degenerate, 22 and HM + Fisher - stacked SNR contours
eg:

Case 12?
m1,    m2,    t0,D,     phi0,i,   lam,  bet, psi
8.89e5,1.11e5,0, 3.67e4,pi/3,pi/2,3pi/4,pi/3,pi/3

Case 0
